---
title: "WET Sensor QAQC"
author: "Sam Struthers-CSU"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.dim = c(12,10))
#Load Libraries and Plot theme
source("src/setup_libraries.R")
source("src/setup_ross_theme.R")
library(ross.wq.tools)

#functions for wet api pull
source("src/data_collation/pull_wet_api_loveland.R")
# Read in all files in src/sensor_qaqc
walk(list.files("src/sensor_qaqc", full.names = TRUE), source)

```

# Goals

1)  Determine how long the historical record is
2)  Compute seasonal ranges for `ross.wq.tools` input
3)  Run `ross.wq.tools` QAQC on the data and determine if this is sufficient to clean up data
4)  Save this historical record to parquet for future use

## Pull in the Recent Data from the WET API

We can only pull in the last year's worth of data from the WET API, so we will pull in the last year of data for all sites and then combine it with the historical record we have in the `data/raw/sensor` folder.

```{r}
 sites <- c("reservoir_bypass", "sulzer_creek", "big_thompson_narrows", "north_fork")

 current_wet_data <- map_dfr(sites,
                        ~pull_wet_api_loveland(
                          target_site = .x,
                          start_datetime = ymd_hms("2025-01-01 12:00:00", tz = "MST"),
                          end_datetime = Sys.time()
                        ))
 
 
 ggplot(current_wet_data, aes(x = DT_round_MT, y = value, color = site)) +
   geom_line() +
   facet_wrap(~ parameter, scales = "free_y") +
   labs(title = "WET Data from Big Thompson Watershed",
        x = "Date",
        y = "Value",
        color = "Parameter"   
 )
```

```{r}
# Read in historical data and munge
#historical_data <- read_parquet("data/raw/sensor/historical_wet_data.parquet")
historical_data <- tibble() #placeholder

#Munge
all_wet_data <- bind_rows(current_wet_data, historical_data)%>%
  distinct()%>%
  mutate(id = paste(site, parameter, sep = "_"), 
         timestamp = DT_round)%>%
  arrange(site, parameter, DT_round_MT)

write_parquet(all_wet_data, "data/raw/sensor/historical_wet_data.parquet")
```

# Clean up and compute thresholds

```{r}

munged_wet_api <- munge_api_data(api_dir = "data/raw/sensor/")%>%
  filter(parameter %nin% c("salinity", "Actual Conductivity"))%>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)%>%
  map(~tidy_api_data(api_data = .)) %>%
  map(., generate_summary_statistics)

season_thresholds <- map_dfr(munged_wet_api, make_threshold_table)
gc()

```

# Apply flags

```{r}

single_sensor_flags <- munged_wet_api %>%
  map(., ~add_seasonal_flag(df = ., threshold_table = season_thresholds))%>%
  #map(., ~add_repeat_flag(.))%>% # Because of rounding in WET system, this flag overflags real data, so we are not using it for now
  map(., ~add_frozen_flag(.))%>%
  map(.,  ~find_do_noise(df = .))%>%
  map(., ~add_drift_flag(df = .))

gc()

intrasensor_flags <- single_sensor_flags %>%
  rbindlist(fill = TRUE) %>%
  split(by = "site")%>%
  map(., ~intersensor_check(.) )%>%
  map(.,  ~add_burial_flag(.))%>%
  map(., ~add_unsubmerged_flag(., method = "sc"))%>% #Depth data is unreliable here so we can use our SC method to flag unsubmerged data (<10 us/cm)
  rbindlist(fill = TRUE) %>%
  mutate(flag = ifelse(flag == "", NA, flag)) %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  keep(~nrow(.) > 0)

#network list 
site_order_list <- list(
  "big_t" = c("north_fork", "big_thompson_narrows", "csu_canyon_mouth"),
  "reservoir_bypass" = c("reservoir_bypass"),
  "sulzer_creek" = c("sulzer_creek")
)

# apply network-level quality control
network_flags <- intrasensor_flags%>%
  # network check compares patterns across sites
  purrr::map(~ross.wq.tools::network_check(df = ., intrasensor_flags_arg = intrasensor_flags,
                            site_order_arg = site_order_list)) %>% # using site order list from above to determine network connectivity
  rbindlist(fill = TRUE) %>%
  # clean up flag column formatting
  tidy_flag_column() %>%
  split(f = list(.$site, .$parameter), sep = "-") %>%
  # add suspect data flags for isolated anomalies
  purrr::map(~add_suspect_flag(.)) %>%
  rbindlist(fill = TRUE)

```

# Quick Plots to assess quality

```{r}
plots <- network_flags %>%
  split(.$parameter) %>%
  map(~ {
    ggplot(.x, aes(x = DT_round, y = mean, color = flag)) +
      geom_point() +
      facet_wrap(~site, scales = "free_y") +
      labs(title = unique(.x$parameter))
  })

walk(plots, print)

```

Seems like in general, things are working as we would expect! Couple of notes:

- I dropped actual conductivity and salinity from this workflow since they are just transformed SC

- We have Chl-a Fluorescence at Sulzer and Chlorophyll (ug/L) at the other sites

- Depth is only at the Narrows site and seems to be quite wonky. We probably want to use SC as our depth/submerged check

- DO interference/ burial seems to be overflagging slightly so we may want to remove that flag

- Ideally we can get more years of data so our seasonal ranges are not so tight

- Hydrocarbon appears to be very overflagged but I am unfamiliar with this parameter so maybe that is normal?

- Network check does appear to help with the Big Thompson sites and we may want to use it for the two sondes on the canal

## Save Files

```{r}
#save the seasonal thresholds to the derived data folder
write_parquet(season_thresholds, "data/derived/sensor_qaqc/seasonal_thresholds_20260825.parquet")
#save the flagged data to the collated folder
network_flags%>%
  select(site:flag, auto_flag)%>%
  write_parquet("data/collated/sensor/flagged_wet_data_20260825.parquet")

```
